### 2011-01-05 paper.tex
Add first files

\documentclass{llncs}
%
\usepackage{graphicx}
\DeclareGraphicsExtensions{.png}

\newcommand\ignore[1]{}
\newcommand{\imagepathext}[5]{%
\begin{figure}[hbtp]
\hfil\includegraphics[#1]{#2/#3.#4}\hfil
\caption{#5\label{#3}}
\end{figure}}

\newcommand{\image}[3]{\imagepathext{#1}{FIGURES}{#2}{eps}{#3}}
\newcommand{\png}[2]{\imagepathext{width=\columnwidth}{pics}{#1}{png}{#2}}

%

\begin{document}

\frontmatter          % for the preliminaries
\pagestyle{headings}  % switches on printing of running heads
\mainmatter              % start of the contributions
%
\title{A Low-cost Natural Interaction based on a Camera Hand-Gestures Recognizer}
\author{Mohamed-Ikbel Boulabiar\inst{1} \and Thomas Burger\inst{2}
Frank Poirier\inst{2} \and Gilles Coppin\inst{1}}
%
\institute{Telecom Bretagne, Brest, France,\\
\email{boulabiar@gmail.com, gilles.coppin@telecom-bretagne.eu},
\and
Universit\'{e} de Bretagne-Sud, LabSticc, B\^{a}timent, Vannes Cedex, France
\email{thomas.burger|franck.poirier@univ-ubs.fr} }

\maketitle

\begin{abstract}
The abstract should summarize the contents of the paper
using at least 70 and at most 150 words. It will be set in 9-point
font size and be inset 1.0 cm from the right and left margins.
There will be two blank lines before and after the Abstract. \dots
\keywords{natural gesture interaction, low-cost gesture recognition, interactive TV broadcast}
\end{abstract}
%

\section{Introduction}
HCI research focuses more attention than before on enhancing the user experience regarding human-display interaction in order to interact more naturally without the need of clicking on buttons and touching screens. However, in everyday life interaction with home devices having embedded computational power, such as interactive TVs, one does not make benefit of these new interaction paradigms yet.

Testing Refrences \cite{Gesturecraft} and \cite{skinColorSeg}.

\section{Gesture recognition}
First definition of gestures come from the interaction between two human in a discussion, these type of gestures is used to add more precision on the details and according to recent paper, is made by the same mental region of the speech []. An extended meaning come also from gestures language for dumb people.
Gesture recognition got the attention of HCI researchers in order to find better ways to talk to the computer. The first one was the Hand Gestural Cursor (Put-That-There[]) aiming to the simplification of the means of communication between human and the machine.
Since then, the gesture definition included more techniques and got applied on the 2D recognition which is the multi-touch gestures.

\section{Gestures taxonomies}
By looking in the possible gestures human can generate, we get a huge amount of possibilities so there is a need for a taxonomy. Many possible taxonomies exists according to the point of view:

* Taxonomy based on the Gesture Creation Space:
We use this criteria to distinguish between gestures made in the 2D or 3D space.

* Taxonomy based on the number of strokes used in the gesture.
We use this criteria to distinguish between gestures constructed by only one path and between those using many path, so the recognition needs to wait for all strokes before the recognition

* Taxonomy based on gesture use:
We use this technique to distinguish gesture based on the specific use of it, gestures for disabled/dumb people, gestures in talk-shows, gestures in meetings, etc...

\section{Gestures in Talk-shows}
We have analyzed some talk-shows in order to extract important gestures being performed.
(Get the Study from the report + pics + refs)

Steps for skin-color based gesture detection

\subsection{Color Manipulations}
The video processing is based on several modules. First, a basic but adaptive skin color segmentation of a large interval of human skin varieties is performed. 
We do an histogram tuning to better enlarge the colors to all the space available.
Then we transform the color space from BGR to YCrCb because it’s the one with the less parameters where we can do easy segmentation. The transformation from these two color spaces is chosen also because it’s linear []

\begin{center}
\begin{tabular}{c|c|c|c|c}
\textbf{Space} & RGB & HSV & YCrCb & CIE Lab\\
  & R>95, G>40, B>20, & H[0.4 .. 0.7] & Cb[77 .. 127] & C[0 .. 65] \\
\textbf{Param.} & Max\{R,G,B\}-Min\{R,G,B\} < 15 & S[0.15 .. 0.75] & Cr[133 .. 173] & I[0 .. 14] \\
  & abs(R-G) > 15, R > G, R>B & V[0.35 .. 0.95] & &
\end{tabular}
\end{center}

\subsection{Input Filtering}
Then, a morphological kernel is applied to smooth the results, this is necessary to clean the image from lonely pixels and holes inside skin zones.
Each blob is labeled in linear time we use the algorithm [], which requires 1 to 4 passes to recognize all blobs with their bounding path.
We identify the hands and the head by a calibration focused on their first position in the screen. We identify them and add a tag to their respective blobs.

\subsection{Blob Detection}
After having the hand and head blobs identified, an efficient tracking method based on the occlusion is used. It re-triggers a phase of calibration when losing the logic of tracking.
A bounding box distant measure similar to that found in the paper \cite{app06} ("distantBlobTrack"). A distance matrix is also used ('Proximity matrix calculation and "used blob" list initialization') like the one explained in the paper.

When the matrix of distance is set up, there are some loops:
* A loop for detect inactive tracks: those tracks with no blobs near.
* Detect and create new tracks: those blobs without a track near.
* A loop to assign blobs to tracks. It makes clusters with blobs that are close and assign them to a track. In this step some tracks could merge in one.
* At the end, all inactive tracks are checked to delete the old ones.

To better handle blobs, the bounding path of the blobs is simplified to a set of few points when needed, this is used to identify picks for the counter mode.

%Fig. Skin segmentation
% Testing graphics
\png{skincolor}{Skin color}

\section{Simplified gesture generation}
Using these blocks we are able to perturb

\section{Recognition modes}
The output of this video processing is the input of the recognition module, which is based on the blob location on the screen. Four different modes are defined according to the hand locations and the switch between them is based on the grammar:

1. The movement mode:
it is activated when two hands are close to each other, so that the user selects between 4 directions. This mode can be used as input for games to select between the directions.

2. The mouse mode:
it is used to control a cursor to select something in an arbitrary place on the screen. With this mode, we only get the input from a sub zone in the screen and map it to the full screen. We use it in a similar way to a computer touchpad.
The user can validate clicks using a tempo on another zone.

3. The counter mode: counts the number of fingers in a pre-selected hand (the left and right hand are automatically discriminated) by counting the peaks in the simplified contour of the blob. This mode can again be used in games for kids.

4. The multi-touch mode, where we consider the similarities between 2D gestures in a tactile multi-touch context and gestures in the 3D space. To do so, we consider the hands blobs in a manner similar to that of two finger tips in the input of a multi-touch device. Based on that, we can recognize well known multi-touch gestures, such as Drag, Pinch/Zoom and Rotate but applied on our case.

\section{Usability analysis and tests}

% ---- Bibliography ----
\bibliographystyle{splncs03}
\bibliography{paper}

\end{document}

### 2011-01-06 paper.tex
fix authors

@@
 \author{Mohamed-Ikbel Boulabiar\inst{1} \and Thomas Burger\inst{2}
-Frank Poirier\inst{2} \and Gilles Coppin\inst{1}}
+Franck Poirier\inst{3} \and Gilles Coppin\inst{1}}
 %
-\institute{Telecom Bretagne, Brest, France,\\
+\institute{LAB-STICC, Telecom-Bretagne, France,\\
 \email{boulabiar@gmail.com, gilles.coppin@telecom-bretagne.eu},
 \and
-Universit\'{e} de Bretagne-Sud, LabSticc, B\^{a}timent, Vannes Cedex, France
-\email{thomas.burger|franck.poirier@univ-ubs.fr} }
+LAB-STICC, University of Bretagne-Sud, France
+\email{thomas.burger@univ-ubs.fr}
+\and
+VALORIA, University of Bretagne-Sud, France
+\email{franck.poirier@univ-ubs.fr}
+}
 

### 2011-01-21 paper.tex
add gestures family pic
Add Gilles notes

@@
 \usepackage{graphicx}
-\DeclareGraphicsExtensions{.png}
+\DeclareGraphicsExtensions{.eps}
 
@@
 
-\newcommand{\image}[3]{\imagepathext{#1}{FIGURES}{#2}{eps}{#3}}
+\newcommand{\image}[3]{\imagepathext{#1}{pics}{#2}{eps}{#3}}
 \newcommand{\png}[2]{\imagepathext{width=\columnwidth}{pics}{#1}{png}{#2}}
@@
 
-Testing Refrences \cite{Gesturecraft} and \cite{skinColorSeg}.
+We present in this paper an approach that could allow the detection and the interpretation of gestures of a TV spectator from a simple and low cost camera. 
+The final objective of this study is to control the animations of an avatar that should be inserted within a TV show beside the presentator or actor [RevTV]
 
-\section{Gesture recognition}
+ref \cite{Gesturecraft} and \cite{skinColorSeg}.
+
+\section{Gesture Semantics and Recognition}
+Semantics of gestures has been studied when analysing the interaction of a user explaining a story. 
 First definition of gestures come from the interaction between two human in a discussion, these type of gestures is used to add more precision on the details and according to recent paper, is made by the same mental region of the speech [].
@@
 
-\section{Gestures in Talk-shows}
-We have analyzed some talk-shows in order to extract important gestures being performed.
+\section{Gestures Library}
+We have analyzed some talk-shows in order to extract important gestures being performed, and defining a benchmark scenario. 
+We have tried to target the following kinds of gestures in a first step:
+
+\ignore{
 (Get the Study from the report + pics + refs)
+}
+
+\png{handg}{Family of supported gestures}
 
 Steps for skin-color based gesture detection
+
+\section{Technical Aspects}
+Pipeline of the work:
+\png{pipeline}{Pipeline of work components}
+
+\subsection{Used Material}
+Technical aspects of the camera, and used framerate.
+
+\ignore{
+60 Hz, 640x480
+}
 
@@
 A distance matrix is also used ('Proximity matrix calculation and "used blob" list initialization') like the one explained in the paper.
-
+\ignore{
 When the matrix of distance is set up, there are some loops:
@@
 * At the end, all inactive tracks are checked to delete the old ones.
-
+}
 To better handle blobs, the bounding path of the blobs is simplified to a set of few points when needed, this is used to identify picks for the counter mode.
@@
 
+\ignore{
 \section{Simplified gesture generation}
 Using these blocks we are able to perturb
+}
 
@@
 
-\section{Usability analysis and tests}
+\section{Usability analysisn Naturelness and tests}
+
+Naturelness came from the analysis of gestures used in talk shows.
+(gesutures used many times means nature gestures)
+Reverse thinking.
+
+Usability in the context of RevTV ??
 

### 2011-01-24 paper.tex
modify the pipeline pic and the abstract

@@
 \begin{abstract}
+The search for new simplified interaction techniques is always treated as a
+manner to advance the communication with intelligent devices.
+In this paper we present our work to generate intelligent TVs modules capable of
+recognizing human gestures through a low-cost camera.
+We recognize gestures by the tracking of human skin blobs and analyzing the 
+corresponding movements to control a TV in an ubiquitous computing environment.
+Then we present a new gesture library generated after an analysis of TV's Talk-shows.
+
+\ignore{
 The abstract should summarize the contents of the paper
@@
 There will be two blank lines before and after the Abstract. \dots
+}
 \keywords{natural gesture interaction, low-cost gesture recognition, interactive TV broadcast}
@@
 \section{Gestures taxonomies}
-By looking in the possible gestures human can generate, we get a huge amount of possibilities so there is a need for a taxonomy. Many possible taxonomies exists according to the point of view:
+By looking in the possible gestures human can generate, we get a huge amount of possibilities so there is a need for a taxonomy. Many possible taxonomies exist according to the point of view:
 
@@
 * Taxonomy based on the number of strokes used in the gesture.
-We use this criteria to distinguish between gestures constructed by only one path and between those using many path, so the recognition needs to wait for all strokes before the recognition
+We use this criteria to distinguish between gestures constructed by only one path and between those using many paths, so the recognition needs to wait for all strokes before the recognition
 
@@
 We use this technique to distinguish gesture based on the specific use of it, gestures for disabled/dumb people, gestures in talk-shows, gestures in meetings, etc...
+
+Nous avons choisi celle-ci, car elle correspond aux besoins que nous avons identifier dans les scenarios d'utilisation de la télé interactive
 
@@
 \png{handg}{Family of supported gestures}
+\ignore{
+Explanation of the figures
 
 Steps for skin-color based gesture detection
-
+}
 \section{Technical Aspects}
@@
 
-\subsection{Used Material}
-Technical aspects of the camera, and used framerate.
+\subsection{Used Materials}
+We have chosen a low-cost camera for our work to be able to integrate it with other components in the future.
+The PS3Eye camera matched our expectations with a 640x480 resolution combined with a 60 Frame-per-second.
 
 \ignore{
-60 Hz, 640x480
 }
@@
 Naturelness came from the analysis of gestures used in talk shows.
-(gesutures used many times means nature gestures)
+(gestures used many times means nature gestures)
 Reverse thinking.

### 2011-01-24 paper.tex
fix many paragraphs, restructure the document

@@
 }
-\keywords{natural gesture interaction, low-cost gesture recognition, interactive TV broadcast}
+\keywords{natural gesture interaction, low-cost gesture recognition, interactive TV broadcast, ubiquitous computing}
 \end{abstract}
@@
 We present in this paper an approach that could allow the detection and the interpretation of gestures of a TV spectator from a simple and low cost camera. 
-The final objective of this study is to control the animations of an avatar that should be inserted within a TV show beside the presentator or actor [RevTV]
+The final objective of this study is to control the animations of an avatar that should be inserted within a TV show beside the presenter or actor [RevTV].
 
-ref \cite{Gesturecraft} and \cite{skinColorSeg}.
+\section{Gesture Semantics}
+First sources of gestures can come from the interaction between two human in a
+discussion, these type of gestures are used to add more precision on the details
+and they are made by the same mental region of the speech \cite{SymbolicGest}.
 
-\section{Gesture Semantics and Recognition}
-Semantics of gestures has been studied when analysing the interaction of a user explaining a story. 
-First definition of gestures come from the interaction between two human in a discussion, these type of gestures is used to add more precision on the details and according to recent paper, is made by the same mental region of the speech [].
-An extended meaning come also from gestures language for dumb people.
-Gesture recognition got the attention of HCI researchers in order to find better ways to talk to the computer.
-The first one was the Hand Gestural Cursor (Put-That-There[]) aiming to the simplification of the means of communication between human and the machine.
-Since then, the gesture definition included more techniques and got applied on the 2D recognition which is the multi-touch gestures.
+Semantics of gestures have been also studied by the analysis of the movements of
+a user explaining a story \cite{gestureThought}.
+These gestures are called gesticulations and are always accompanying a speech.
 
-\section{Gestures taxonomies}
-By looking in the possible gestures human can generate, we get a huge amount of possibilities so there is a need for a taxonomy. Many possible taxonomies exist according to the point of view:
+This semantics can be divided into two parts:
 
-* Taxonomy based on the Gesture Creation Space:
-We use this criteria to distinguish between gestures made in the 2D or 3D space.
+\begin{description}
+ \item[Animation Gestures] used to animate a virtual avatar.
+ \item[Command Gestures] used to launch a specific predefined action.
+\end{description}
 
-* Taxonomy based on the number of strokes used in the gesture.
-We use this criteria to distinguish between gestures constructed by only one path and between those using many paths, so the recognition needs to wait for all strokes before the recognition
+\ignore{
+Gesture recognition got the attention of HCI researchers in order to find better
+ways to talk to the computer. The first one was the Hand Gestural Cursor
+(Put-That-There[]) aiming to the simplification of the means of communication
+between human and the machine.
+Since then, the gesture definition included more techniques and got applied on
+the 2D recognition which is the multi-touch gestures.
+}
 
-* Taxonomy based on gesture use:
-We use this technique to distinguish gesture based on the specific use of it, gestures for disabled/dumb people, gestures in talk-shows, gestures in meetings, etc...
+\subsection{Gestures taxonomies}
+By looking in the possible gestures human can generate\cite{Gesturecraft}, we
+get a huge amount of possibilities so there is a need for a taxonomy.
+Many possible taxonomies exist according to the technical or analytical aspects:
+\begin{description}
+ \item[Gesture Creation Space:] We use this criteria to distinguish between gestures made in the 2D or 3D space.
+ \item[Number of used strokes:] We use this criteria to distinguish between gestures constructed by only one path and between those using many paths, so the recognition needs to wait for all strokes before the recognition
+ \item[Gesture use:] We use this technique to distinguish gesture based on the specific use of it, gestures for disabled people, gestures in talk-shows, gestures in meetings.
+% \item[]
+% \item[]
+\end{description}
 
-Nous avons choisi celle-ci, car elle correspond aux besoins que nous avons identifier dans les scenarios d'utilisation de la télé interactive
+%Gesture and Thoughts, page 18
+\begin{description}
+ \item[Gesticulation] is motion that embodies a meaning relatable to the
+accompanying speech. It is made chiefly with the arms and hands but is not
+restricted to these body parts
+ \item[Speech-linked gestures] are parts of sentences themselves, the gesture completes the sentence structure.
+ \item[Emblems] are conventionalized signs, such as thumbs-up or the ring (first
+finger and thumb tips touching, other fingers extended) for ``OK.''
+ \item[Pantomime] is dumb show, a gesture or sequence of gestures conveying a
+narrative line, with a story to tell, produced without speech.
+\end{description}
 
-\section{Gestures Library}
+We have chosen to analyze gesticulations as they are the most frequent.
+%, and project them on the technical taxonomies.
+And we have also made our own extraction from Talk-Shows.
+
+%Nous avons choisi celle-ci, car elle correspond aux besoins que nous avons identifier dans les scenarios d'utilisation de la télé interactive
+
+\subsection{Gestures Library}
 We have analyzed some talk-shows in order to extract important gestures being performed, and defining a benchmark scenario. 
@@
 
+\png{handg}{Family of supported gestures}
+
+The figure.\ref{handg} shows our supported gestures. We provide a movement mode
+used to select directions, then a command mode, then a hand fingers recognition,
+and in the end a cursor movement mode.
+
 \ignore{
-(Get the Study from the report + pics + refs)
+Explanation of the figures
+Steps for skin-color based gesture detection
 }
 
-\png{handg}{Family of supported gestures}
-\ignore{
-Explanation of the figures
-
-Steps for skin-color based gesture detection
-}
-\section{Technical Aspects}
+\newpage
+\section{Technical Work}
 Pipeline of the work:
@@
 We have chosen a low-cost camera for our work to be able to integrate it with other components in the future.
-The PS3Eye camera matched our expectations with a 640x480 resolution combined with a 60 Frame-per-second.
+The PS3Eye camera matched our expectations with a 640x480 resolution combined with a 60 frames-per-second capability.
 
@@
 \subsection{Color Manipulations}
-The video processing is based on several modules. First, a basic but adaptive skin color segmentation of a large interval of human skin varieties is performed. 
+The video processing is based on several modules. First, a basic but adaptive skin color segmentation of a large interval of human skin varieties is performed \cite{skinColorSeg}.
 We do an histogram tuning to better enlarge the colors to all the space available.
@@
 
-\section{Recognition modes}
+\section{Gestural informations and Recognition modes}
 The output of this video processing is the input of the recognition module, which is based on the blob location on the screen.
@@
 3.
-The counter mode: counts the number of fingers in a pre-selected hand (the left and right hand are automatically discriminated) by counting the peaks in the simplified contour of the blob.
+The counter mode: counts the number of fingers in a preselected hand (the left and right hand are automatically discriminated) by counting the peaks in the simplified contour of the blob.
 This mode can again be used in games for kids.
@@
 
-\section{Usability analysisn Naturelness and tests}
+We have used four modes a first core with the possibility to add more sub-gestures in the future.
+This core will be used to control a children game having to select, choose, and answer basic questions.
+We have stick to that scenario to produce these gestures.
 
-Naturelness came from the analysis of gestures used in talk shows.
+-- add screenshot of the work --
+
+\section{Usability and Naturalness in an ubiquitous environment}
+
+The usability of our system should be compared to other system in an ubiquitous
+environment. In such case, we don't have a full PC where we need to work as in
+the front of a computer, but in the front of a TV.
+The gestures in such environment, and specially for children game scenario,
+are made for a short period of time, and doesn't require a good usability,
+even if we can recognize gestures in real-time.
+
+The Naturalness of gestures is supported by the analysis of gestures to be
+supported and the choice of gesticulation.
+Gesticulation are the most common gestures, so they inherit from this their
+ability to be produced with less complication.
+
+-- to be extended --
+
+\ignore{
+Naturalness came from the analysis of gestures used in talk shows.
 (gestures used many times means nature gestures)
 Reverse thinking.
-
 Usability in the context of RevTV ??
-
+}
 % ---- Bibliography ----

### 2011-01-24 paper.tex
fix figure position

@@
 \subsection{Gestures Library}
-We have analyzed some talk-shows in order to extract important gestures being performed, and defining a benchmark scenario. 
-We have tried to target the following kinds of gestures in a first step:
 
 \png{handg}{Family of supported gestures}
+
+We have analyzed some talk-shows in order to extract important gestures being performed, and defining a benchmark scenario. 
+%We have tried to target the following kinds of gestures in a first step.
 
@@
 
-\newpage
 \section{Technical Work}

### 2011-01-28 paper.tex
Fix Franck points

@@
 The search for new simplified interaction techniques is always treated as a
-manner to advance the communication with intelligent devices.
-In this paper we present our work to generate intelligent TVs modules capable of
+manner to advance the communication with interactive devices.
+In this paper we present our work to generate interactive TVs modules capable of
 recognizing human gestures through a low-cost camera.
@@
 discussion, these type of gestures are used to add more precision on the details
-and they are made by the same mental region of the speech \cite{SymbolicGest}.
+and they are made by the same auditory areas of the cortex \cite{SymbolicGest}.
 
@@
 \subsection{Gestures taxonomies}
-By looking in the possible gestures human can generate\cite{Gesturecraft}, we
+By looking in the possible gestures human can generate \cite{Gesturecraft}, we
 get a huge amount of possibilities so there is a need for a taxonomy.
@@
  \item[Number of used strokes:] We use this criteria to distinguish between gestures constructed by only one path and between those using many paths, so the recognition needs to wait for all strokes before the recognition
- \item[Gesture use:] We use this technique to distinguish gesture based on the specific use of it, gestures for disabled people, gestures in talk-shows, gestures in meetings.
+ \item[Gesture use:] We use this criteria to distinguish gesture based on the specific use of it, gestures for disabled people, gestures in talk-shows, gestures in meetings.
 % \item[]
@@
 \end{description}
-
 %Gesture and Thoughts, page 18
 \begin{description}
- \item[Gesticulation] is motion that embodies a meaning relatable to the
+ \item[Gesticulation] is motion that embodies a meaning reliable to the
 accompanying speech. It is made chiefly with the arms and hands but is not
-restricted to these body parts
+restricted to these body parts.
  \item[Speech-linked gestures] are parts of sentences themselves, the gesture completes the sentence structure.
@@
 
-The figure.\ref{handg} shows our supported gestures. We provide a movement mode
+The figure\ref{handg} shows our supported gestures. We provide a movement mode
 used to select directions, then a command mode, then a hand fingers recognition,
@@
 
-\subsection{Color Manipulations}
+\subsection{Color Transformations}
 The video processing is based on several modules. First, a basic but adaptive skin color segmentation of a large interval of human skin varieties is performed \cite{skinColorSeg}.
@@
 Then we transform the color space from BGR to YCrCb because it’s the one with the less parameters where we can do easy segmentation.
-The transformation from these two color spaces is chosen also because it’s linear []
+The transformation from these two color spaces is chosen also because it’s linear \cite{skinColorSeg}.
 
 \begin{center}
-\begin{tabular}{c|c|c|c|c}
-\textbf{Space} & RGB & HSV & YCrCb & CIE Lab\\
+\begin{tabular}{|c|c|c|c|c|}
+\textbf{Space} & BGR & HSV & YCrCb & CIE Lab\\
   & R>95, G>40, B>20, & H[0.4 .. 0.7] & Cb[77 .. 127] & C[0 .. 65] \\
@@
 \subsection{Input Filtering}
-Then, a morphological kernel is applied to smooth the results, this is necessary to clean the image from lonely pixels and holes inside skin zones.
-Each blob is labeled in linear time we use the algorithm [], which requires 1 to 4 passes to recognize all blobs with their bounding path.
+Then, a morphological kernel is applied to smooth the results, this is necessary
+to clean the image from lonely pixels and holes inside skin zones.
+Each blob is labeled in linear time we use the algorithm \cite{CompLabeling} , which requires 1 to 4 passes to recognize all blobs with their bounding path.
 We identify the hands and the head by a calibration focused on their first position in the screen. We identify them and add a tag to their respective blobs.
@@
 
-We have used four modes a first core with the possibility to add more sub-gestures in the future.
+We have used four modes in a first core with the possibility to add more sub-gestures in the future.
 This core will be used to control a children game having to select, choose, and answer basic questions.
@@
 
+\section{}
+
 \ignore{

### 2011-01-28 paper.tex
Add Gilles comments

@@
 \newcommand{\imagepathext}[5]{%
-\begin{figure}[hbtp]
+\begin{figure}[!htbp]
 \hfil\includegraphics[#1]{#2/#3.#4}\hfil
@@
 We present in this paper an approach that could allow the detection and the interpretation of gestures of a TV spectator from a simple and low cost camera. 
-The final objective of this study is to control the animations of an avatar that should be inserted within a TV show beside the presenter or actor [RevTV].
+%The final objective of this study is to control the animations of an avatar that should be inserted within a TV show beside the presenter or actor [RevTV].
+One major scenario why we rely on corresponds to educational games here a pupil
+could control his/her avatar in a program led by a ``real'' TV animator.
+This kind of scenarios needs to be able to manage commands interaction
+like pointing, selecting and moving as well as natural gesture animation.
 
@@
 get a huge amount of possibilities so there is a need for a taxonomy.
-Many possible taxonomies exist according to the technical or analytical aspects:
+%Many possible taxonomies exist according to the technical or analytical aspects:
+In order to describe and analyse each gesture, we can rely on the following
+aspects:
 \begin{description}
@@
 %Gesture and Thoughts, page 18
+According to McNail \cite{gestureThought}, it is possible and useful to
+distinguish between these gestures:
 \begin{description}
@@
 restricted to these body parts.
- \item[Speech-linked gestures] are parts of sentences themselves, the gesture completes the sentence structure.
+ \item[Speech-linked gestures] are parts of sentences themselves, the gesture
+completes the sentence structure.
  \item[Emblems] are conventionalized signs, such as thumbs-up or the ring (first
@@
 
-We have chosen to analyze gesticulations as they are the most frequent.
+In our work, we focalize on emblems commands and gesticulations.
+%We have chosen to analyze gesticulations as they are the most frequent.
 %, and project them on the technical taxonomies.
-And we have also made our own extraction from Talk-Shows.
-
+%And we have also made our own extraction from Talk-Shows.
 %Nous avons choisi celle-ci, car elle correspond aux besoins que nous avons identifier dans les scenarios d'utilisation de la télé interactive
@@
 
+In order to identify relevant gestures we have analyzed some talk-shows in order to extract important gestures being performed, and defining a benchmark scenario. 
+%We have tried to target the following kinds of gestures in a first step.
+
 \png{handg}{Family of supported gestures}
-
-We have analyzed some talk-shows in order to extract important gestures being performed, and defining a benchmark scenario. 
-%We have tried to target the following kinds of gestures in a first step.
 
@@
 and in the end a cursor movement mode.
+\pagebreak 
+We have selected to support 4 basic gestures to be extended depending on the
+context fulfilling the requirements of a benchmark scenario.
 
@@
 \section{Technical Work}
+
 Pipeline of the work:
+
 \png{pipeline}{Pipeline of work components}
@@
 The PS3Eye camera matched our expectations with a 640x480 resolution combined with a 60 frames-per-second capability.
+This camera costs about 40\$ which is a reasonable price for a potential market deployment.
 
@@
 \begin{center}
-\begin{tabular}{|c|c|c|c|c|}
+\begin{tabular}{|l|c|c|c|c|}
+\hline
 \textbf{Space} & BGR & HSV & YCrCb & CIE Lab\\
+\hline
  & R>95, G>40, B>20, & H[0.4 .. 0.7] & Cb[77 .. 127] & C[0 .. 65] \\
 \textbf{Param.} & Max\{R,G,B\}-Min\{R,G,B\} < 15 & S[0.15 .. 0.75] & Cr[133 .. 173] & I[0 .. 14] \\
-  & abs(R-G) > 15, R > G, R>B & V[0.35 .. 0.95] & &
+ & abs(R-G) > 15, R > G, R>B & V[0.35 .. 0.95] & & \\
+\hline
 \end{tabular}
@@
 
-\subsection{Blob Detection}
+\subsection{Blobs Detection}
 After having the hand and head blobs identified, an efficient tracking method based on the occlusion is used. It re-triggers a phase of calibration when losing the logic of tracking.
@@
 -- add screenshot of the work --
+%\pngl{point}{simplify}{List of modes}
+
+\begin{figure}[!htb]
+\centering
+  \includegraphics[width=0.45\textwidth]{./pics/point.png}
+  \includegraphics[width=0.4\textwidth]{./pics/simplify.png}
+  \caption{List of modes}
+%  \label{fig:Gestes}
+\end{figure}
 
@@
 
-\section{}
+\section{System integration of this interaction and future work}
+--
+
+Gesture + facial recog.
+Voice recognition
+Haptic 
+--
 

### 2011-02-01 paper.tex
Thomas rmsq

@@
 manner to advance the communication with interactive devices.
-In this paper we present our work to generate interactive TVs modules capable of
+In this paper, we present our work to generate interactive TVs modules capable of
 recognizing human gestures through a low-cost camera.
@@
 corresponding movements to control a TV in an ubiquitous computing environment.
-Then we present a new gesture library generated after an analysis of TV's Talk-shows.
+Then, we present a new gesture library generated after an analysis of TV's Talk-shows.
 
@@
 \subsection{Gestures taxonomies}
-By looking in the possible gestures human can generate \cite{Gesturecraft}, we
-get a huge amount of possibilities so there is a need for a taxonomy.
+By looking at the possible gestures human can generate \cite{Gesturecraft}, we
+get a huge amount of possibilities. So, there is a need for a taxonomy.
 %Many possible taxonomies exist according to the technical or analytical aspects:
@@
 \begin{description}
- \item[Gesticulation] is motion that embodies a meaning reliable to the
+ \item[Gesticulation] is a motion that embodies a meaning reliable to the
 accompanying speech. It is made chiefly with the arms and hands but is not
@@
 
-The figure\ref{handg} shows our supported gestures. We provide a movement mode
+Figure\ref{handg} shows our supported gestures. We provide a movement mode
 used to select directions, then a command mode, then a hand fingers recognition,
-and in the end a cursor movement mode.
+and, finally, a cursor movement mode.
 \pagebreak 
@@
 \subsection{Used Materials}
-We have chosen a low-cost camera for our work to be able to integrate it with other components in the future.
+We have chosen a low-cost camera for our work that can be integrated with other components in the future.
 The PS3Eye camera matched our expectations with a 640x480 resolution combined with a 60 frames-per-second capability.
-This camera costs about 40\$ which is a reasonable price for a potential market deployment.
+This camera costs about 40\$, which is a reasonable price for a potential market deployment.
 
@@
 The video processing is based on several modules. First, a basic but adaptive skin color segmentation of a large interval of human skin varieties is performed \cite{skinColorSeg}.
-We do an histogram tuning to better enlarge the colors to all the space available.
-Then we transform the color space from BGR to YCrCb because it’s the one with the less parameters where we can do easy segmentation.
-The transformation from these two color spaces is chosen also because it’s linear \cite{skinColorSeg}.
+We also use a histogram equalisation technique to better enlarge the colors to all the space available.
+Then we transform the color space from BGR to YCrCb, as it’s the most adapted one to skin segmentation
+Moreover, the corresponding transformation is linear \cite{skinColorSeg}.
 
@@
 \subsection{Input Filtering}
-Then, a morphological kernel is applied to smooth the results, this is necessary
-to clean the image from lonely pixels and holes inside skin zones.
-Each blob is labeled in linear time we use the algorithm \cite{CompLabeling} , which requires 1 to 4 passes to recognize all blobs with their bounding path.
+During the next step, a morphological kernel is applied to smooth the results, this is necessary
+to clean the image from isolated pixels and holes inside skin zones.
+Each blob is labeled in linear time using the algorithm described in \cite{CompLabeling} , which requires 1 to 4 passes to recognize all blobs with their bounding path.
 We identify the hands and the head by a calibration focused on their first position in the screen. We identify them and add a tag to their respective blobs.
@@
 }
-To better handle blobs, the bounding path of the blobs is simplified to a set of few points when needed, this is used to identify picks for the counter mode.
+To better handle blobs, the bounding path of the blobs is simplified to a set of few points when needed. This is used to identify picks for the counter mode.
 
@@
 The output of this video processing is the input of the recognition module, which is based on the blob location on the screen.
-Four different modes are defined according to the hand locations and the switch between them is based on the grammar:
+Four different modes are defined according to the hand locations.
+The switch between them is based on the following grammar:
 

### 2011-02-02 paper.tex
fix problems

@@
 manner to advance the communication with interactive devices.
-In this paper, we present our work to generate interactive TVs modules capable of
-recognizing human gestures through a low-cost camera.
+In this paper, we present our work to generate interactive TVs modules capable
+of recognizing human gestures through the PS3Eye low-cost camera.
 We recognize gestures by the tracking of human skin blobs and analyzing the 
 corresponding movements to control a TV in an ubiquitous computing environment.
-Then, we present a new gesture library generated after an analysis of TV's Talk-shows.
+We also present a new free gestures icons library created to allow easy
+representation and diagramming.
+%after an analysis of TV's Talk-shows.
 
-\ignore{
-The abstract should summarize the contents of the paper
-using at least 70 and at most 150 words. It will be set in 9-point
-font size and be inset 1.0 cm from the right and left margins.
-There will be two blank lines before and after the Abstract. \dots
-}
-\keywords{natural gesture interaction, low-cost gesture recognition, interactive TV broadcast, ubiquitous computing}
+\keywords{natural gesture interaction, low-cost gesture recognition, interactive
+TV broadcast, ubiquitous computing}
 \end{abstract}
@@
 %The final objective of this study is to control the animations of an avatar that should be inserted within a TV show beside the presenter or actor [RevTV].
-One major scenario why we rely on corresponds to educational games here a pupil
-could control his/her avatar in a program led by a ``real'' TV animator.
+One major scenario that we rely on, corresponds to educational games where a pupil
+controls his/her avatar in a program led by a ``real'' TV animator.
 This kind of scenarios needs to be able to manage commands interaction
@@
 This semantics can be divided into two parts:
-
 \begin{description}
@@
 By looking at the possible gestures human can generate \cite{Gesturecraft}, we
-get a huge amount of possibilities. So, there is a need for a taxonomy.
+get a huge amount of possibilities which depend on the context and on the type.
+%So, there is a need for a taxonomy.
 %Many possible taxonomies exist according to the technical or analytical aspects:
-In order to describe and analyse each gesture, we can rely on the following
-aspects:
-\begin{description}
+%In order to describe and analyse each gesture, we can rely on the following aspects:
+\ignore{\begin{description}
  \item[Gesture Creation Space:] We use this criteria to distinguish between gestures made in the 2D or 3D space.
  \item[Number of used strokes:] We use this criteria to distinguish between gestures constructed by only one path and between those using many paths, so the recognition needs to wait for all strokes before the recognition
- \item[Gesture use:] We use this criteria to distinguish gesture based on the specific use of it, gestures for disabled people, gestures in talk-shows, gestures in meetings.
-% \item[]
-% \item[]
-\end{description}
+ \item[Gesture context:] We use this criteria to distinguish gesture based on the specific use of it, gestures for disabled people, gestures in talk-shows, gestures in meetings.
+\end{description}}
 %Gesture and Thoughts, page 18
 According to McNail \cite{gestureThought}, it is possible and useful to
-distinguish between these gestures:
+distinguish between these gestures and a possbile taxonomy can provide us these
+types:
 \begin{description}
@@
 
-In order to identify relevant gestures we have analyzed some talk-shows in order to extract important gestures being performed, and defining a benchmark scenario. 
+In order to identify relevant gestures we have analyzed some talk-shows in order
+to extract most frequent gestures being performed.
+According to our scenario of use in the context of Interacrive TV.
+%and defining a benchmark scenario.
 %We have tried to target the following kinds of gestures in a first step.
@@
 
-\ignore{
-Explanation of the figures
-Steps for skin-color based gesture detection
-}
-
 \section{Technical Work}
 
-Pipeline of the work:
+Modules Pipeline used to extract gestural informations:
 
@@
 \hline
- & R>95, G>40, B>20, & H[0.4 .. 0.7] & Cb[77 .. 127] & C[0 .. 65] \\
-\textbf{Param.} & Max\{R,G,B\}-Min\{R,G,B\} < 15 & S[0.15 .. 0.75] & Cr[133 .. 173] & I[0 .. 14] \\
- & abs(R-G) > 15, R > G, R>B & V[0.35 .. 0.95] & & \\
+ & R\textgreater 95, G\textgreater 40, B\textgreater 20, & H[0.4 .. 0.7] & Cb[77 .. 127] & C[0 .. 65] \\
+\textbf{Param.} & Max\{R,G,B\}-Min\{R,G,B\}\textless 15 & S[0.15 .. 0.75] & Cr[133 .. 173] & I[0 .. 14] \\
+ & abs(R-G)\textgreater 15, R\textgreater G, R\textgreater B & V[0.35 .. 0.95] & & \\
 \hline
@@
 \subsection{Input Filtering}
-During the next step, a morphological kernel is applied to smooth the results, this is necessary
-to clean the image from isolated pixels and holes inside skin zones.
+During this step, a morphological kernel is applied to smooth the results,
+this is necessary to clean the image from isolated pixels and holes inside skin
+zones.
+
+\subsection{Blobs Detection}
 Each blob is labeled in linear time using the algorithm described in \cite{CompLabeling} , which requires 1 to 4 passes to recognize all blobs with their bounding path.
@@
 
-\subsection{Blobs Detection}
+%Fig. Skin segmentation
+% Testing graphics
+\png{skincolor}{Skin color}
+\section{Blobs Tracking}
 After having the hand and head blobs identified, an efficient tracking method based on the occlusion is used. It re-triggers a phase of calibration when losing the logic of tracking.
@@
 
-%Fig. Skin segmentation
-% Testing graphics
-\png{skincolor}{Skin color}
-
-\ignore{
-\section{Simplified gesture generation}
-Using these blocks we are able to perturb
-}
-
 \section{Gestural informations and Recognition modes}
-The output of this video processing is the input of the recognition module, which is based on the blob location on the screen.
+The output of the video processing is the input of the recognition module, which is based on the blob location on the screen.
 Four different modes are defined according to the hand locations.
@@
 
-The Naturalness of gestures is supported by the analysis of gestures to be
+The Naturalness of gestures is supported by the analysis of those to be
 supported and the choice of gesticulation.
-Gesticulation are the most common gestures, so they inherit from this their
+Gesticulation are the most common ones, so they inherit from this their
 ability to be produced with less complication.
 
--- to be extended --
+Emblems gestures which englobe commands, are choisen to be produced in more
+difficult positions to allow easy descrimination from gesticulations.
+
+Spacial gestural interactions always lack from the feedback for the interaction.
+This affects also the usability because the user can no more be guided in space
+as he was with surface movement or simple physical joysticks.
 
 \section{System integration of this interaction and future work}
---
 
+Our system support gestural interaction at the moment but other multimodal ways
+to fine tune the input and give the user feedback are possible.
+These possible evolution of the system are possible:
+
+\begin{description}
+ \item[Facial Recognition]: our system don't take care of the facial expressions
+recogntions. A future support in this area can be added for more reactiveness in
+pupil's games.
+ \item[Voice Recognition]: To speed up commands handling, we can use short voice
+keywords either to move from one mode to another, or to select object.
+ \item[Haptic feedback]: A special wearable vest can be used to allow more
+reactiveness with the user. But this area still lacking innovation because the
+haptic feedback is by area and not continue.
+\end{description}
+
+\ignore{
 Gesture + facial recog.
@@
 --
-
-\ignore{
 Naturalness came from the analysis of gestures used in talk shows.

### 2011-02-03 paper.tex
more fixes

@@
 \section{Introduction}
-HCI research focuses more attention than before on enhancing the user experience regarding human-display interaction in order to interact more naturally without the need of clicking on buttons and touching screens.
-However, in everyday life interaction with home devices having embedded computational power, such as interactive TVs, one does not make benefit of these new interaction paradigms yet.
+HCI research focuses more attention than before on enhancing the user experience
+regarding human-display interaction in order to interact more naturally without
+the need of clicking on buttons and touching screens. However, in everyday life
+interaction with home devices having embedded computational power, such as
+interactive TVs, one does not make benefit of these new interaction paradigms yet.
 
-We present in this paper an approach that could allow the detection and the interpretation of gestures of a TV spectator from a simple and low cost camera. 
-%The final objective of this study is to control the animations of an avatar that should be inserted within a TV show beside the presenter or actor [RevTV].
-One major scenario that we rely on, corresponds to educational games where a pupil
-controls his/her avatar in a program led by a ``real'' TV animator.
+We present in this paper an approach that could allow the detection and the
+interpretation of gestures of a TV spectator from a simple and low cost camera. 
+RevTV is the name of the French project for adding new interaction techniques
+to TVs to allow the inclusion of the telespectator.
+%The final objective of this study is to control the animations of an avatar
+%that should be inserted within a TV show beside the presenter or actor [RevTV].
+Its major scenario which we rely on, corresponds to educational games where a
+pupil controls his/her avatar in a program led by a ``real'' TV animator.
 This kind of scenarios needs to be able to manage commands interaction
@@
 \section{Gesture Semantics}
+Gestures do not come alone, they are combined with speech, or with cognitive
+activity. We study in this part the sources of gestures and the relation between
+them and other activities.
 First sources of gestures can come from the interaction between two human in a
@@
 
-Figure\ref{handg} shows our supported gestures. We provide a movement mode
-used to select directions, then a command mode, then a hand fingers recognition,
+Fig.\ref{handg} shows our supported gestures. We provide a movement mode
+used to select the 4 directions, then a multitouch nthen a command mode, then a hand fingers recognition,
 and, finally, a cursor movement mode.
-\pagebreak 
-We have selected to support 4 basic gestures to be extended depending on the
-context fulfilling the requirements of a benchmark scenario.
+%\pagebreak 
+We have selected 4 basic gestures modes to be supported in our system as a first step.
+Then to be extended depending on the context fulfilling the requirements
+of our scenario.
 
@@
 
-Modules Pipeline used to extract gestural informations:
+In the figure \ref{pipeline}, we show the pipeline of the modules used to
+extract gestural informations. Each part is described in details in the next
+subsections.
 
@@
 
-\ignore{
-}
+\subsection{Color Transformations}
+The video processing is based on several modules.
+First, a basic but adaptive skin color segmentation of a large interval of human skin varieties is performed \cite{skinColorSeg}.
+We also use a histogram equalisation technique to better enlarge the colors to all the space available.
+Then we transform the color space from BGR, which come from the camera to YCrCb,
+as it’s the most adapted one to skin segmentation
+Moreover, the corresponding transformation is linear \cite{skinColorSeg}.
 
-\subsection{Color Transformations}
-The video processing is based on several modules. First, a basic but adaptive skin color segmentation of a large interval of human skin varieties is performed \cite{skinColorSeg}.
-We also use a histogram equalisation technique to better enlarge the colors to all the space available.
-Then we transform the color space from BGR to YCrCb, as it’s the most adapted one to skin segmentation
-Moreover, the corresponding transformation is linear \cite{skinColorSeg}.
+Other color spaces like HSV or CIE-Lab can be used for skin color segmentation,
+but the transformation from BGR either takes more time or needs more parameters
+in the next step.
 
@@
 \subsection{Input Filtering}
-During this step, a morphological kernel is applied to smooth the results,
+During this step, a 5x5 opening morphological kernel \cite{morphologicalAnalysis} is applied to smooth the results,
 this is necessary to clean the image from isolated pixels and holes inside skin
@@
 \subsection{Blobs Detection}
-Each blob is labeled in linear time using the algorithm described in \cite{CompLabeling} , which requires 1 to 4 passes to recognize all blobs with their bounding path.
-We identify the hands and the head by a calibration focused on their first position in the screen. We identify them and add a tag to their respective blobs.
+Each blob is labeled in linear time using the contour tracing technique with
+the linear-time component-labeling algorithm \cite{CompLabeling},
+which requires 1 to 4 passes to recognize all blobs with their bounding contour.
+We identify the hands and the head by a calibration focused on their first
+position in the screen. We identify them and add a tag to their respective blobs.
 
@@
 \section{Blobs Tracking}
-After having the hand and head blobs identified, an efficient tracking method based on the occlusion is used. It re-triggers a phase of calibration when losing the logic of tracking.
-A bounding box distant measure similar to that found in the paper \cite{app06} ("distantBlobTrack").
-A distance matrix is also used ('Proximity matrix calculation and "used blob" list initialization') like the one explained in the paper.
-\ignore{
-When the matrix of distance is set up, there are some loops:
-* A loop for detect inactive tracks: those tracks with no blobs near.
-* Detect and create new tracks: those blobs without a track near.
-* A loop to assign blobs to tracks. It makes clusters with blobs that are close and assign them to a track. In this step some tracks could merge in one.
-* At the end, all inactive tracks are checked to delete the old ones.
-}
-To better handle blobs, the bounding path of the blobs is simplified to a set of few points when needed. This is used to identify picks for the counter mode.
+After having the hands and head blobs identified, an efficient
+tracking method based on the apparence model for occlusion handling\cite{app06}.
+We have used the cvblob implementation \cite{cvblob} for that algorithm which 
+stores the mesures of bounding boxes distance and provide tracks instead of just blobs.  %distantBlobTrack.
+
+When the matrix of distance is set up, the coming loops
+are executed to handle blobs changes:
+\begin{itemize}
+ \item A loop to detect inactive tracks: those tracks with no blobs near.
+ \item Detect and create new tracks: those blobs without a track near.
+ \item A loop to assign blobs to tracks. It makes clusters with blobs that are close and assign them to a track.
+In this step some tracks could merge in one.
+ \item A last loop which check all inactive tracks to delete the old ones.
+\end{itemize}
+
+To better handle blobs, the bounding path of the blobs
+is simplified to a set of few points when needed.
+This is used to identify picks for the counter mode.
 
 \section{Gestural informations and Recognition modes}
-The output of the video processing is the input of the recognition module, which is based on the blob location on the screen.
-Four different modes are defined according to the hand locations.
-The switch between them is based on the following grammar:
-
-1. The movement mode:
-it is activated when two hands are close to each other, so that the user selects between 4 directions. This mode can be used as input for games to select between the directions.
-
-2. The mouse mode:
-it is used to control a cursor to select something in an arbitrary place on the screen.
+The output of the video processing is the input of the recognition module,
+which is based on the track location on the screen.
+Four different modes are defined according to the hand locations. The switch between them is based on the following grammar:
+\begin{description}
+ \item[The movement mode:] it is activated when two hands are close to each other, so that the user selects between 4 directions.
+This mode can be used as input for games to select between the directions.
+ \item[The multi-touch mode:] where we consider the similarities between 2D gestures in a tactile multi-touch context and gestures in the 3D space.
+To do so, we consider the hands blobs in a manner similar to that of two finger tips in the input of a multi-touch device.
+Based on that, we can recognize well known multi-touch gestures, such as Drag, Pinch/Zoom and Rotate but applied on our case.
+ \item[The counter mode:] counts the number of fingers in a preselected hand (the left and right hand are automatically discriminated) by counting the peaks in the simplified contour of the blob.
+This mode can again be used in games for kids.
+ \item[The mouse mode:] it is used to control a cursor to select something in an arbitrary place on the screen.
 With this mode, we only get the input from a sub zone in the screen and map it to the full screen.
@@
 The user can validate clicks using a tempo on another zone.
+\end{description}
 
-3.
-The counter mode: counts the number of fingers in a preselected hand (the left and right hand are automatically discriminated) by counting the peaks in the simplified contour of the blob.
-This mode can again be used in games for kids.
-
-4.
-The multi-touch mode, where we consider the similarities between 2D gestures in a tactile multi-touch context and gestures in the 3D space.
-To do so, we consider the hands blobs in a manner similar to that of two finger tips in the input of a multi-touch device.
-Based on that, we can recognize well known multi-touch gestures, such as Drag, Pinch/Zoom and Rotate but applied on our case.
-
+A phase of calibration is triggered when the logic of tracking is lost or damaged.
 We have used four modes in a first core with the possibility to add more sub-gestures in the future.
@@
 
--- add screenshot of the work --
 %\pngl{point}{simplify}{List of modes}
@@
   \includegraphics[width=0.4\textwidth]{./pics/simplify.png}
+  \includegraphics[width=0.46\textwidth]{./pics/fingers.png}
+  \includegraphics[width=0.46\textwidth]{./pics/move.png}
   \caption{List of modes}
@@
 
-The usability of our system should be compared to other system in an ubiquitous
-environment. In such case, we don't have a full PC where we need to work as in
-the front of a computer, but in the front of a TV.
+The usability of our system should be compared to other systems in an ubiquitous
+environment. In our case, we have a TV instead of a PC.
 The gestures in such environment, and specially for children game scenario,

### 2011-02-04 paper.tex
Thomas Last night remarks

@@
 %
-\title{A Low-cost Natural Interaction based on a Camera Hand-Gestures Recognizer}
+\title{A Low-cost Natural Interaction System based on a Camera Hand-Gestures Recognizer}
 \author{Mohamed-Ikbel Boulabiar\inst{1} \and Thomas Burger\inst{2}
@@
 \begin{abstract}
-The search for new simplified interaction techniques is always treated as a
-manner to advance the communication with interactive devices.
-In this paper, we present our work to generate interactive TVs modules capable
+The search for new simplified interaction techniques is 
+mainly motiviated by the improvements of 
+the communication with interactive devices.
+In this paper, we present an interactive TVs module capable
 of recognizing human gestures through the PS3Eye low-cost camera.
 We recognize gestures by the tracking of human skin blobs and analyzing the 
-corresponding movements to control a TV in an ubiquitous computing environment.
+corresponding movements. It provides means to control a TV in an ubiquitous computing environment.
 We also present a new free gestures icons library created to allow easy
@@
 \section{Introduction}
-HCI research focuses more attention than before on enhancing the user experience
-regarding human-display interaction in order to interact more naturally without
-the need of clicking on buttons and touching screens. However, in everyday life
-interaction with home devices having embedded computational power, such as
-interactive TVs, one does not make benefit of these new interaction paradigms yet.
+HCI research focuses more attention than before on enhancing the user
+experience regarding human-display interaction in order to interact
+more naturally without the need of clicking on buttons and touching screens.
+However, in everyday life, interaction with home devices having
+embedded computational power, such as interactive TVs,
+one does not make benefit from these new interaction paradigms yet.
 
@@
 to TVs to allow the inclusion of the telespectator.
+%Pourquoi as-tu enlevé cette phrase (ligne suivante) ? Cela me semblait une bonne introduction à la présentation du projet.
+
+%The final objective of this study is to control the animations of an avatar that should be inserted within a TV show beside the presenter or actor [RevTV].
+One major scenario that we rely on, corresponds to some educational game where a pupil
+controls his/her avatar which interact in a forecast program led by a ``real'' TV animator.
+During such kind of scenarios, commands interaction
+like pointing, selecting and moving, as well as natural gesture animation, are required.
+
+\ignore{
 %The final objective of this study is to control the animations of an avatar
@@
 like pointing, selecting and moving as well as natural gesture animation.
+}
+% Il faut rajouter une description du projet Rev-TV
 
@@
 \end{description}
+%%%
+% toute cette partie me semble incompréhensible... (entre la debut de la section 2 et la début de la 2.1)
+% Je veux bien t'aider à la rédiger, mais je ne comprends pas vraiment ce que tu veux dire... 
+% Quel est ton message ?
 
@@
 \subsection{Gestures taxonomies}
-By looking at the possible gestures human can generate \cite{Gesturecraft}, we
-get a huge amount of possibilities which depend on the context and on the type.
+A rapid look the possible gestures human can perform \cite{Gesturecraft}, lead to the conclusion that the amount of possibilities is tremoundous.
+Nonetheless, the gestures can be classified according to various criteria.
+Here, we consider a taxonomy based on the context of the gestures as well as on their types:
+%%%%%%%
+%By looking at the possible gestures human can generate \cite{Gesturecraft}, we
+%get a huge amount of possibilities which depend on the context and on the type.
+
 %So, there is a need for a taxonomy.
@@
 
-In our work, we focalize on emblems commands and gesticulations.
+In our work, we focalize on emblems commands and gesticulations, as both of them are of prime importance for the scenario under consideration.
 %We have chosen to analyze gesticulations as they are the most frequent.
@@
 
+% Il faut rédiger complétement cette partie... C'est pas compréhensible, et il n'y a pas de verbe dans la seconde phrase.
 In order to identify relevant gestures we have analyzed some talk-shows in order
@@
 
-Fig.\ref{handg} shows our supported gestures. We provide a movement mode
-used to select the 4 directions, then a multitouch nthen a command mode, then a hand fingers recognition,
+Figure\ref{handg} shows our supported gestures. We provide a movement mode
+used to select the 4 directions, then a multitouch, then a command mode, then a hand fingers recognition,
 and, finally, a cursor movement mode.
@@
 
-\subsection{Color Transformations}
-The video processing is based on several modules.
+\subsection{Color Transformations} %%%%%%%%%%%%%%%%%%%
+The video processing is based on several modules, such as illustrated in Fig ... .
 First, a basic but adaptive skin color segmentation of a large interval of human skin varieties is performed \cite{skinColorSeg}.
@@
 Then we transform the color space from BGR, which come from the camera to YCrCb,
-as it’s the most adapted one to skin segmentation
-Moreover, the corresponding transformation is linear \cite{skinColorSeg}.
+as it is the most adapted one to skin segmentation
+Moreover, the corresponding transformation is linear \cite{skinColorSeg}, which helps computation time saving.
 
@@
 \subsection{Input Filtering}
-During this step, a 5x5 opening morphological kernel \cite{morphologicalAnalysis} is applied to smooth the results,
-this is necessary to clean the image from isolated pixels and holes inside skin
+During this step, a 5x5 opening morphological kernel \cite{morphologicalAnalysis} is applied to smooth the results.
+Practically, it cleans the image from isolated pixels and holes inside skin
 zones.

### 2011-02-04 paper.tex
Add references + Fix Text

@@
 The search for new simplified interaction techniques is 
-mainly motiviated by the improvements of 
+mainly motivated by the improvements of 
 the communication with interactive devices.
@@
 We recognize gestures by the tracking of human skin blobs and analyzing the 
-corresponding movements. It provides means to control a TV in an ubiquitous computing environment.
+corresponding movements. It provides means to control a TV in an ubiquitous
+computing environment.
 We also present a new free gestures icons library created to allow easy
@@
 HCI research focuses more attention than before on enhancing the user
-experience regarding human-display interaction in order to interact
-more naturally without the need of clicking on buttons and touching screens.
+experience regarding human-display interaction.
+This area of research and specifically gesture, work on making interact natural
+without the need of clicking on buttons and touching screens with first systems
+since the 1980's \cite{Bolt1980}, \cite{Pavlovic97visinter}, \cite{Derpanisreview}.
 However, in everyday life, interaction with home devices having
@@
 ways to talk to the computer. The first one was the Hand Gestural Cursor
-(Put-That-There[]) aiming to the simplification of the means of communication
+(Put-That-There) aiming to the simplification of the means of communication
 between human and the machine.
@@
 \subsection{Gestures taxonomies}
-A rapid look the possible gestures human can perform \cite{Gesturecraft}, lead to the conclusion that the amount of possibilities is tremoundous.
-Nonetheless, the gestures can be classified according to various criteria.
+A rapid look the possible gestures human can perform \cite{Gesturecraft},
+lead to the conclusion that the amount of possibilities is tremendous.
+Nonetheless, the gestures can be classified according to various criteria not
+only to simplify their recognition, but also to allow their reproducing on an
+avatar to putting tags on them for future analysis\cite{gestureRecreation}.
 Here, we consider a taxonomy based on the context of the gestures as well as on their types:
@@
 According to McNail \cite{gestureThought}, it is possible and useful to
-distinguish between these gestures and a possbile taxonomy can provide us these
+distinguish between these gestures and a possible taxonomy can provide us these
 types:
@@
 
-In our work, we focalize on emblems commands and gesticulations, as both of them are of prime importance for the scenario under consideration.
+In our work, we focalize on emblems commands and gesticulations, as both of them
+are of prime importance for the scenario under consideration.
 %We have chosen to analyze gesticulations as they are the most frequent.
@@
 
-% Il faut rédiger complétement cette partie... C'est pas compréhensible, et il n'y a pas de verbe dans la seconde phrase.
+% Il faut rédiger complétement cette partie...
+%C'est pas compréhensible, et il n'y a pas de verbe dans la seconde phrase.
 In order to identify relevant gestures we have analyzed some talk-shows in order
 to extract most frequent gestures being performed.
-According to our scenario of use in the context of Interacrive TV.
+According to our scenario of use in the context of Interactive TV.
 %and defining a benchmark scenario.
@@
 
-\png{handg}{Family of supported gestures}
+\png{handg}{Family of supported gestures represented using the free gestures icons library from https://github.com/boulabiar/ishara }
 
@@
 The Naturalness of gestures is supported by the analysis of those to be
-supported and the choice of gesticulation.
-Gesticulation are the most common ones, so they inherit from this their
+supported and the preference of gesticulations.
+Gesticulations are the most common gestures, so they inherit from this their
 ability to be produced with less complication.
 
-Emblems gestures which englobe commands, are choisen to be produced in more
-difficult positions to allow easy descrimination from gesticulations.
+Emblems gestures which englobe commands, are chosen to be produced in more
+difficult positions to allow easy discrimination from gesticulations.
+Even with these extractions, the naturalness aspect of the gestural interaction
+itself are still objected.  \cite{naturalNorman2010}
 
@@
 
-Our system support gestural interaction at the moment but other multimodal ways
-to fine tune the input and give the user feedback are possible.
+Our system support gestural interaction at the moment but the integration of
+other multimodal ways are possible to fine tune the input and give the user
+feedback.
 These possible evolution of the system are possible:

### 2011-02-04 paper.tex
add CCL + some refs

@@
 to TVs to allow the inclusion of the telespectator.
-%Pourquoi as-tu enlevé cette phrase (ligne suivante) ? Cela me semblait une bonne introduction à la présentation du projet.
 
-%The final objective of this study is to control the animations of an avatar that should be inserted within a TV show beside the presenter or actor [RevTV].
+The final objective of this study is to control the animations of an avatar
+that should be inserted within a TV show beside the presenter or actor.
 One major scenario that we rely on, corresponds to some educational game where a pupil
@@
 
-\ignore{
-%The final objective of this study is to control the animations of an avatar
-%that should be inserted within a TV show beside the presenter or actor [RevTV].
-Its major scenario which we rely on, corresponds to educational games where a
-pupil controls his/her avatar in a program led by a ``real'' TV animator.
-This kind of scenarios needs to be able to manage commands interaction
-like pointing, selecting and moving as well as natural gesture animation.
-}
 % Il faut rajouter une description du projet Rev-TV
+%Le dernier paragraphe n'est pas une description ?
 
 \section{Gesture Semantics}
+Symbolic gestures, such as emblems, play an important role in human
+communication as they can fully take the place of words.
+These gestures and spoken language are processed by the same system in the human brain.
+
+Results support a model in which bilateral modality-specific areas in superior and inferior temporal cortices extract salient features from vocal-auditory and gestural-visual stimuli respectively.
+However, both classes of stimuli activate a common, left-lateralized network of inferior frontal and posterior temporal regions in which symbolic gestures and spoken words may be mapped onto common, corresponding conceptual representations.
+
 Gestures do not come alone, they are combined with speech, or with cognitive
@@
 %get a huge amount of possibilities which depend on the context and on the type.
-
 %So, there is a need for a taxonomy.
@@
 
-%Fig. Skin segmentation
-% Testing graphics
 \png{skincolor}{Skin color}
+
 \section{Blobs Tracking}
 After having the hands and head blobs identified, an efficient
-tracking method based on the apparence model for occlusion handling\cite{app06}.
+tracking method based on the appearance model for occlusion handling\cite{app06}.
 We have used the cvblob implementation \cite{cvblob} for that algorithm which 
-stores the mesures of bounding boxes distance and provide tracks instead of just blobs.  %distantBlobTrack.
+stores the measures of bounding boxes distance and provide tracks instead of just blobs.  %distantBlobTrack.
 
@@
 \section{System integration of this interaction and future work}
+Human brain perisylvian areas, identified as the core of the brain's language
+system, are not in fact committed to language processing, but may function as a
+modality-independent semiotic system that plays a broader role in human
+communication, linking meaning with symbols whether these are words, gestures,
+images, sounds, or objects \cite{SymbolicGest}.
+This natural handling of multimodal communications gives an argument to build
+recognizer taking part of most of these modalities specially to remove ambiguous
+gesture meaning decision cases.
 
-Our system support gestural interaction at the moment but the integration of
-other multimodal ways are possible to fine tune the input and give the user
-feedback.
+Our system only supports gestural interaction at the moment but the integration
+of other multimodal means are possible to fine tune the input and give the user
+better feedback.
 These possible evolution of the system are possible:
@@
 
-\ignore{
-Gesture + facial recog.
-Voice recognition
-Haptic 
---
-Naturalness came from the analysis of gestures used in talk shows.
-(gestures used many times means nature gestures)
-Reverse thinking.
-Usability in the context of RevTV ??
-}
+\section*{Conclusion}
+In this paper we have shown a proof-of-concept mechanism to recognize hand
+gestures then use them to control a TV or to take actions in a Game scenario.
+We have also freely provided a library which can be used to represent gestures
+in other scenarios.
+The evolution of our system is being discussed to add more modalities even if we
+are aware of some of the limits \cite{Oviatt99tenmyths}.
+
 % ---- Bibliography ----

### 2011-02-04 paper.tex
final corrections

@@
 
-Results support a model in which bilateral modality-specific areas in superior and inferior temporal cortices extract salient features from vocal-auditory and gestural-visual stimuli respectively.
-However, both classes of stimuli activate a common, left-lateralized network of inferior frontal and posterior temporal regions in which symbolic gestures and spoken words may be mapped onto common, corresponding conceptual representations.
+Gestures do not come alone, they are combined with speech, or with cognitive
+activities which can be detected from the interaction between two human in a
+discussion, these type of gestures are used to add more precision on the details
+and they are made by the same areas of the cortex \cite{SymbolicGest}.
 
-Gestures do not come alone, they are combined with speech, or with cognitive
-activity. We study in this part the sources of gestures and the relation between
-them and other activities.
-First sources of gestures can come from the interaction between two human in a
-discussion, these type of gestures are used to add more precision on the details
-and they are made by the same auditory areas of the cortex \cite{SymbolicGest}.
+% We study in this part the sources of gestures and the relation between
+%them and other activities.
 
-Semantics of gestures have been also studied by the analysis of the movements of
-a user explaining a story \cite{gestureThought}.
-These gestures are called gesticulations and are always accompanying a speech.
+We try to extract some semantics of gestures by the analysis of the movements of
+a user explaining a story and searching for a relation between gestures and the
+part of the story being told \cite{gestureThought}.
+%The result of this is the extraction of gesticulations .
 
-This semantics can be divided into two parts:
+After extraction, most of gestures semantics can be divided into two parts for
+their possible future use as:
 \begin{description}
@@
 
-In our work, we focalize on emblems commands and gesticulations, as both of them
-are of prime importance for the scenario under consideration.
+In our work, we focalize on emblems for commands and gesticulations, as both of
+them are of prime importance for the scenario under consideration.
 %We have chosen to analyze gesticulations as they are the most frequent.
@@
 %And we have also made our own extraction from Talk-Shows.
-%Nous avons choisi celle-ci, car elle correspond aux besoins que nous avons identifier dans les scenarios d'utilisation de la télé interactive
+%Nous avons choisi celle-ci, car elle correspond aux besoins que nous avons
+%identifié dans les scenarios d'utilisation de la télé interactive
 
@@
 to extract most frequent gestures being performed.
-According to our scenario of use in the context of Interactive TV.
+According to our scenario of use in the context of Interactive TV, we need
+gesture to trigger commands but also for natural interaction with the avatar.
+We have created a vector based gestures icons to represent them.
+These 4 icons in the figure\ref{handg}, which are part of the ``ishara'' library,
+represent the software supported gestures in our application.
 %and defining a benchmark scenario.
@@
 
-\png{pipeline}{Pipeline of work components}
+\png{pipeline}{Pipeline of the work components showing the routing and
+transformation of the camera information until getting the gestural informations
+ready to use in the scenario}
 
@@
 
-\png{skincolor}{Skin color}
+\png{skincolor}{A representation of different human skin color variations}
 
@@
 To do so, we consider the hands blobs in a manner similar to that of two finger tips in the input of a multi-touch device.
-Based on that, we can recognize well known multi-touch gestures, such as Drag, Pinch/Zoom and Rotate but applied on our case.
+Based on that, we can recognize well known multi-touch gestures, such as Drag, Pinch/Zoom and Rotate with a consideration of a interaction centroid\cite{CentroidGest} but applied in our case.
  \item[The counter mode:] counts the number of fingers in a preselected hand (the left and right hand are automatically discriminated) by counting the peaks in the simplified contour of the blob.
@@
   \includegraphics[width=0.46\textwidth]{./pics/move.png}
-  \caption{List of modes}
+  \caption{A sub-list of recognition modes showing pointing, number of hand
+fingers counting and the movement mode}
 %  \label{fig:Gestes}

### 2011-02-04 paper.tex
Last Franck and Thomas notes

@@
 \frontmatter % for the preliminaries
-\pagestyle{headings}  % switches on printing of running heads
+\pagestyle{empty} % switches on printing of running heads
 \mainmatter % start of the contributions
@@
 experience regarding human-display interaction.
-This area of research and specifically gesture, work on making interact natural
-without the need of clicking on buttons and touching screens with first systems
-since the 1980's \cite{Bolt1980}, \cite{Pavlovic97visinter}, \cite{Derpanisreview}.
-However, in everyday life, interaction with home devices having
-embedded computational power, such as interactive TVs,
-one does not make benefit from these new interaction paradigms yet.
+This area of research focus on making interaction more natural, so that it is not necessary to click on buttons and to touch screens.
+To do so, automatic gesture recognition is an interesting paradigm \cite{Bolt1980}, \cite{Pavlovic97visinter}, \cite{Derpanisreview}.
+However, in everyday life, for interaction with home devices having
+embedded computational power, such as interactive TVs, one does not make benefit from these new interaction paradigms yet.
 
-We present in this paper an approach that could allow the detection and the
+We present in this paper an approach that allows the detection and the
 interpretation of gestures of a TV spectator from a simple and low cost camera.
-RevTV is the name of the French project for adding new interaction techniques
-to TVs to allow the inclusion of the telespectator.
+this work takes place in the context of the French FUI\footnote{Fond Unique Interministeriel} Project RevTV,  the aim of which is to add new interaction techniques, sos that telespectators take activaly part to the TV broadcast.
+The final objective of this project is to control the animations of an avatar
+that should be inserted within a TV show beside the presenter or actor.
+By now, the major scenario that we rely on, corresponds to some educational game where a pupil
+controls her or his avatar which interacts in a broadcast program led by a ``real'' TV animator.
+During such kind of scenarios, commands interaction like pointing, selecting and moving, as well as natural gesture animation, are required.
 
-The final objective of this study is to control the animations of an avatar
-that should be inserted within a TV show beside the presenter or actor.
-One major scenario that we rely on, corresponds to some educational game where a pupil
-controls his/her avatar which interact in a forecast program led by a ``real'' TV animator.
-During such kind of scenarios, commands interaction
-like pointing, selecting and moving, as well as natural gesture animation, are required.
-
-% Il faut rajouter une description du projet Rev-TV
-%Le dernier paragraphe n'est pas une description ?
+The paper is organized as following.
+Section 2 presents the study held on gestures
+semantics, sources, and taxonomies and include the presentation of the free
+icons library created and used.
+Section 3 shows the technical details of handling the camera input for gestures recognition.
+Section 4 shows the modes where the gestural informations generated are used
+with some screenshots of the running application.
+Section 5 answers the usability and naturelness question of the use of gestures
+specially in an ubiquitous environment.
+Finally section 6 discusses the future of the work and the possible integration of
+other multimodal modules.
 
@@
 communication as they can fully take the place of words.
-These gestures and spoken language are processed by the same system in the human brain.
-
-Gestures do not come alone, they are combined with speech, or with cognitive
-activities which can be detected from the interaction between two human in a
-discussion, these type of gestures are used to add more precision on the details
-and they are made by the same areas of the cortex \cite{SymbolicGest}.
+These gestures are processed by the same area of the human brain as the spoken language \cite{SymbolicGest}.
+Hence, these gesures do not come alone, and they are often combined with speech, or with cognitive
+activities, as they are classically used to add more precision on the details of a talk.
 
@@
 
-We try to extract some semantics of gestures by the analysis of the movements of
-a user explaining a story and searching for a relation between gestures and the
-part of the story being told \cite{gestureThought}.
-%The result of this is the extraction of gesticulations .
-
-After extraction, most of gestures semantics can be divided into two parts for
+We have extracted some semantics of such type of gestures, by the analysis of the movements of
+a user explaining a story, and by searching for a relation between gestures and the
+part of the story being told \cite{gestureThought}. After extraction, most of gestures semantics can be divided into two parts for
 their possible future use as:
@@
 \end{description}
-%%%
-% toute cette partie me semble incompréhensible... (entre la debut de la section 2 et la début de la 2.1)
-% Je veux bien t'aider à la rédiger, mais je ne comprends pas vraiment ce que tu veux dire... 
-% Quel est ton message ?
 
@@
 According to McNail \cite{gestureThought}, it is possible and useful to
-distinguish between these gestures and a possible taxonomy can provide us these
-types:
+distinguish between these gestures. Here follows a possible taxonomy :
 \begin{description}
@@
 
-In our work, we focalize on emblems for commands and gesticulations, as both of
-them are of prime importance for the scenario under consideration.
+In our work, we focus on Emblems for Command Gestures, and on Gesticulations for Animation Gestures.
 %We have chosen to analyze gesticulations as they are the most frequent.
@@
 %C'est pas compréhensible, et il n'y a pas de verbe dans la seconde phrase.
-In order to identify relevant gestures we have analyzed some talk-shows in order
-to extract most frequent gestures being performed.
-According to our scenario of use in the context of Interactive TV, we need
-gesture to trigger commands but also for natural interaction with the avatar.
+In order to identify relevant gestures we have analyzed some talk-shows, and we have extracted the most frequent gestures being performed.
+According to our scenario of use in the context of interactive TV (RevTV project), we need some
+gesture to trigger commands, aas well as other gestures to implement natural interaction with the avatar.
 We have created a vector based gestures icons to represent them.
-These 4 icons in the figure\ref{handg}, which are part of the ``ishara'' library,
-represent the software supported gestures in our application.
+These 4 icons, represented in figure \ref{handg}, are part of the \textbf{ishara} library \cite{ishara}.  They
+represent the gestures supported by the software of our application. We provide a movement mode, a multitouch mode, a command mode, a hand fingers recognition,
+and, finally, a cursor movement mode (see Section 5 for detailled explanation of these modes).
 %and defining a benchmark scenario.
@@
 
-\png{handg}{Family of supported gestures represented using the free gestures icons library from https://github.com/boulabiar/ishara }
+\png{handg}{Family of supported gestures represented using the free gestures icons library from \cite{ishara}}
 
-Figure\ref{handg} shows our supported gestures. We provide a movement mode
-used to select the 4 directions, then a multitouch, then a command mode, then a hand fingers recognition,
-and, finally, a cursor movement mode.
 %\pagebreak
-We have selected 4 basic gestures modes to be supported in our system as a first step.
-Then to be extended depending on the context fulfilling the requirements
+These five basic gestures modes are already supported in our system as a first step. They will be extended depending on the context fulfilling the requirements
 of our scenario.
@@
 
-In the figure \ref{pipeline}, we show the pipeline of the modules used to
+Figure \ref{pipeline} is a description of the pipeline of the modules used to
 extract gestural informations. Each part is described in details in the next
@@
 
-\subsection{Used Materials}
-We have chosen a low-cost camera for our work that can be integrated with other components in the future.
+\subsection{Camera Input}
+We have chosen a low-cost camera that can be integrated with other components in the future.
 The PS3Eye camera matched our expectations with a 640x480 resolution combined with a 60 frames-per-second capability.
@@
 
-\subsection{Color Transformations} %%%%%%%%%%%%%%%%%%%
-The video processing is based on several modules, such as illustrated in Fig ... .
+\subsection{Colors Transformations} %%%%%%%%%%%%%%%%%%%
+The video processing which depend on the OpenCV library \cite{openCVlib} is based on several modules, such as illustrated in figure \ref{pipeline}.
 First, a basic but adaptive skin color segmentation of a large interval of human skin varieties is performed \cite{skinColorSeg}.
-We also use a histogram equalisation technique to better enlarge the colors to all the space available.
+We also perform histogram equalization technique to better enlarge the colors to all the space available.
 Then we transform the color space from BGR, which come from the camera to YCrCb,
-as it is the most adapted one to skin segmentation
-Moreover, the corresponding transformation is linear \cite{skinColorSeg}, which helps computation time saving.
-
-Other color spaces like HSV or CIE-Lab can be used for skin color segmentation,
-but the transformation from BGR either takes more time or needs more parameters
-in the next step.
+as it is the most adapted one to skin segmentation. Other color spaces like HSV or CIE-Lab can be used for skin color segmentation,
+but the transformation from BGR either takes more time (the transformation we use is linear) or needs more parameters
+in the next step \cite{skinColorSeg}.
 
@@
 
-\section{Blobs Tracking}
+\subsection{Blobs Tracking}
 After having the hands and head blobs identified, an efficient
-tracking method based on the appearance model for occlusion handling\cite{app06}.
+tracking method based on appearance model is used \cite{app06}. Let us note that it handles occlusion problems.
 We have used the cvblob implementation \cite{cvblob} for that algorithm which
-stores the measures of bounding boxes distance and provide tracks instead of just blobs.  %distantBlobTrack.
+stores the measures of bounding boxes distance and provides tracks instead of just blobs. %distantBlobTrack.
 
-When the matrix of distance is set up, the coming loops
+Once the matrix of distance is defined, the following loops
 are executed to handle blobs changes:
@@
  \item A loop to detect inactive tracks: those tracks with no blobs near.
- \item Detect and create new tracks: those blobs without a track near.
+ \item A loop to detect and create new tracks: those blobs without a track near.
  \item A loop to assign blobs to tracks. It makes clusters with blobs that are close and assign them to a track.
@@
 is simplified to a set of few points when needed.
-This is used to identify picks for the counter mode.
+This is used to identify picks for the counter mode (see Section 5). Finally, a phase of calibration is triggered when the logic of tracking is lost or damaged.
 
@@
 
-A phase of calibration is triggered when the logic of tracking is lost or damaged.
-We have used four modes in a first core with the possibility to add more sub-gestures in the future.
-This core will be used to control a children game having to select, choose, and answer basic questions.
-We have stick to that scenario to produce these gestures.
+% inutile : on répète ce qui a déjà été dit !
+%We have used four modes in a first core with the possibility to add more sub-gestures in the future.
+%This core will be used to control a children game having to select, choose, and answer basic questions.
+%We have stick to that scenario to produce these gestures.
 
@@
 fingers counting and the movement mode}
-%  \label{fig:Gestes}
+ \label{fig:Gestes}
 \end{figure}
@@
 
-Spacial gestural interactions always lack from the feedback for the interaction.
+Spatial gestural interactions always lack from the feedback for the interaction.
 This affects also the usability because the user can no more be guided in space
@@
 \section{System integration of this interaction and future work}
-Human brain perisylvian areas, identified as the core of the brain's language
+Human brain Broca's area, identified as the core of the brain's language
 system, are not in fact committed to language processing, but may function as a
@@
 In this paper we have shown a proof-of-concept mechanism to recognize hand
-gestures then use them to control a TV or to take actions in a Game scenario.
-We have also freely provided a library which can be used to represent gestures
-in other scenarios.
-The evolution of our system is being discussed to add more modalities even if we
-are aware of some of the limits \cite{Oviatt99tenmyths}.
+gestures then use them to control a TV or to take actions in a Game scenario
+for pupils.
+We have also provided a free library which can be used to represent gestures
+in other scenarios and other studies.
+
+The evolution of our system could be possible in the direction of a multimodal
+environment in the case where we can be aware of the limits and myths
+\cite{Oviatt99tenmyths}.
+But this evolution is a natural choice as new devices are getting more
+computational power and the ubiquitous environment is becoming a reality.
 

### 2011-02-07 paper.tex
last changes

@@
 Section 3 shows the technical details of handling the camera input for gestures recognition.
-Section 4 shows the modes where the gestural informations generated are used
+Section 4 shows the modes where the gestural information generated are used
 with some screenshots of the running application.
@@
 Figure \ref{pipeline} is a description of the pipeline of the modules used to
-extract gestural informations. Each part is described in details in the next
+extract gestural information. Each part is described in details in the next
 subsections.
@@
 \png{pipeline}{Pipeline of the work components showing the routing and
-transformation of the camera information until getting the gestural informations
+transformation of the camera information until getting the gestural information
 ready to use in the scenario}
@@
 
-\section{Gestural informations and Recognition modes}
+\section{Gestural information and Recognition modes}
 The output of the video processing is the input of the recognition module,
